---
title: "Decadal nitrogen addition alters chemical composition of soil organic matter in a boreal forest"
author: "Shun Hasegawa"
date: "Date"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This repository stores the R scripts and data to reproduced the results presented in XXX.

# File description

## R scripts
* **analysis.R**: This loads required packages and data.

* **analysis_correlation.R**: This analyses correlation between leaf $\delta^{15}N$ and the relative abundance of N compound in the pyrolysis products, soil C:N ratio and the relative abundance of N compound in the pyrolysis products and leaf $\delta^{15}N$ and soil C mass.

* **analysis_LCratio.R**: This analyses the association between lignin:carbohydrate ratios in the pyrolysis product and leaf $\delta^{15}N$.

* **analysis_leaf_d15N.R**:  This fits an asymptotic regression line on leaf $\delta^{15}N$ as a function of distance from the edge of the experimental plots.

* **analysis_NMR.R**: Herein, the results of NMR analysis were summarised. Also, redundancy analysis (RDA) is performed on the composition of NMR products to assess its association with leaf $\delta^{15}N$.

* **analysis_pyrolysis.R**: Herein, the results of pyrolysis GC/MS were summarised. Also, RDA is performed on the composition of pyroslysis products to assess its association with leaf $\delta^{15}N$.

## Data
* **Leaf_d15N.csv**: Data on $\delta^{15}N$ in *Vaccinium vitis-idaea* leaves.
* **NMR_spectra_relative_abund.csv**: Relative abundance of NMR products.
* **Pyrolysis_chromatogram_FHhoriz.csv**: Peak area size of chromatogram for the pyrolysis products in the soil samples collected at the F/H horizon.
* **Pyrolysis_chromatogram_Lhoriz.csv**: Peak area size of chromatogram for the pyrolysis products in the soil samples collected at the L horizon.
* **Soil_CN.csv**: 


## Session information
```{r sessioninfo, echo=FALSE, message=FALSE}
source("R/packages.R")
sessionInfo()
```

